Trans-dimensional Bayesian Inference and Nested Sampling

### 2014-08-05 Documents/Talk/content.tex
Sinewave data figure
Galaxy figure

>>>>

\begin{frame}[t]{Motivating Problem I}
\begin{itemize}
\item How many sinusoids are in this data?
\end{itemize}
\begin{center}
\includegraphics[scale=0.35]{sinewave_data.pdf}
\end{center}
\begin{itemize}
\item Also, what are their periods, amplitudes and phases?
\end{itemize}
\end{frame}

\begin{frame}[t]{Motivating Problem II}
\begin{itemize}
\item How many galaxies are in this data?
\end{itemize}
\begin{center}
\includegraphics[scale=0.35]{../Paper/galaxyfield_data.pdf}
\end{center}
\begin{itemize}
\item Also, what are their positions, sizes, orientations, etc?
\end{itemize}
\end{frame}

\begin{frame}[t]{Bayesian Inference 101}
Probabilities describe degrees of plausibility

Uncertain quantities described by probability distributions

\end{frame}
